Missing data: Current practice in football research and recommendations for reporting missingness

### 2020-09-02 paper/paper.Rmd
change wording in the intro

The three categorisations of missingness types provide a useful
framework to describe bias arising from missing data. If you strongly
suspect data is MCAR, you can be more certain your data isn't biased,
otherwise there may be bias in your sample. This does not mean data MAR
or MNAR make data invalid, instead it identifies potential biases, which
can help improve future research design. However, these categorisations
do not necessarily guide the user in their subsequent actions in
analysis, or describe specifically how values go missing. To identify
possible mechanisms for missingness, the data must be explored. It can
be challenging to identify the missingness mechanism in data, but it is
critical, since missing values could change the outcome of a study. This
could mean the work cannot be reproduced, and worse, may lead scientists
and practitioners to the wrong outcome.

>>>>

The three categorisations of missingness types provide a useful
framework to describe bias arising from missing data. If one strongly
suspects data is MCAR, one can be more certain your data isn't biased,
otherwise there may be bias in your sample. This does not mean that data MAR
or MNAR make data invalid, instead it identifies potential biases, which
can help improve future research design **(Nick, can we look at this sentence please)**. However, these categorisations
do not necessarily guide a researcher in their subsequent actions in
analysis, or describe specifically how values go missing. To identify
possible mechanisms for missingness, the data must be explored. It can
be challenging to identify the missingness mechanism in data, but it is
critical, since missing values could change the outcome of a study. This
could mean the work cannot be reproduced, and worse, may lead scientists
and practitioners to the wrong outcome.
